Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-10 draft.tex
minor proof-reading revisions to section 3

\item \emph{For both players $g$ and $s$, $\frac {Q_{i0}}{1-\delta} \geq  -\zeta_i+\frac{W_{i0}(p_{1i}) + L_{i0}(1-p_{1i})}{1-\delta}$: the expected outcome under war is worse than the status quo at the beginning of the game.}

@@

Player $c$ dislikes war and so will never invest in $w_s$ or $w_g$, which only serve to increase the likelihood that one of the inside actors chooses to fight. It would also not want to make the government lose and so won't invest in $l_g$. This leaves three state variables in which player $c$ might invest: $q_s$, $q_g$, $l_s$.

@@

In equilibrium, the outside actors' investments are paired: the patron's investments in the secessionists' status quo payoffs deter player $c$'s investments in the secessionists' payoffs from ceding. Likewise, investments by player $c$ in the government's status quo payoffs deter the patron from investing in the government's payoffs from ceding. Investments by player $c$ in the secessionists' status quo payoffs deter the patron from investing in the secessionists' payoffs from winning the conflict via fighting. In each case, the investments are sufficient to make the largest continuation payoffs in the game between the secessionists and the government those from playing status quo.

@@

The strategies for the government and secessionists in this equilibrium are to play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted below, playing Status Quo is the best response for both inside actors. The strategies for the insides actors are the following, organized according to the patron's investments in each relevant state variable. In period $t$:

@@

	\item As long as $R_{pt} \leq \frac{1}{p_{1s}} \left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right]$ to augment $w_{s,t}$, player $c$ invests $R_{ct} = R_{pt}p_{1s} + \mu - Q_{s,t-1} + \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$ in $q_{st}$. Similar to case two, the outcome is that investments in $w_{st}$ and $q_{st}$ are zero.

If $R_{pt} > \frac{1}{p_{1s}}\left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right] $ to augment $w_{s,t}$, player $c$ will choose $R_{ct}=0$. Fight becomes the unique best response for the secessionists.
\end{enumerate}
\end{definition}

>>>>

\item \textit{For both players $g$ and $s$, $\frac {Q_{i0}}{1-\delta} \geq  -\zeta_i+\frac{W_{i0}(p_{1i}) + L_{i0}(1-p_{1i})}{1-\delta}$: the expected outcome under war is worse than the status quo at the beginning of the game.}

@@

Player $c$ dislikes war and so will never invest in $w_s$ or $w_g$ since they increase the likelihood that one of the inside actors chooses to fight. It would also not want to make the government lose and so won't invest in $l_g$. This leaves three state variables in which player $c$ might invest: $q_s$, $q_g$, $l_s$.

@@

In equilibrium, the outside actors' investments are paired: the patron's investments in the secessionists' status quo payoffs deter player $c$'s investments in the secessionists' payoffs from ceding. Likewise, investments by player $c$ in the government's status quo payoffs deter the patron from investing in the government's payoffs from ceding. Investments by player $c$ in the secessionists' status quo payoffs deter the patron from investing in the secessionists' payoffs from winning the conflict via fighting. In each case, the potential  investments are such that the largest continuation payoffs in the game between the secessionists and the government those from playing status quo.

@@

The strategies for the government and secessionists in this equilibrium are to play their best responses in the stage game given the continuation values induced by the investments of the outside actors. Unless otherwise noted below, playing Status Quo is the best response for both inside actors.

The strategies for the insides actors are the following, organized according to the patron's investments in each relevant state variable. In period $t$:

@@

	\item As long as $R_{pt} \leq \frac{1}{p_{1s}} \left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right]$ to augment $w_{st}$, player $c$ invests $R_{ct} = R_{pt}p_{1s} + \mu - Q_{s,t-1} + \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)$ in $q_{st}$. Similar to case two, the outcome is that investments in $w_{st}$ and $q_{st}$ are zero.

If $R_{pt} > \frac{1}{p_{1s}}\left[\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de} - \mu + Q_{s,t-1} - \left(-\zeta_{s}(1-\de) + W_{s,t-1}p_{1s} + L_{s,t-1}(1-p_{1s})\right)\right] $ to augment $w_{st}$, player $c$ will choose $R_{ct}=0$. Fight becomes the unique best response for the secessionists.
\end{enumerate}
\end{definition}
